---
title: "Assignment-4"
author: "Vaishnavi Bihare"
date: "4/23/2020"
output: word_document
---

```{r}
library('ISLR')
library("gam")
library('boot')
data("Auto")
```

There’s no direct way to answer if there are nonlinear realtionships between any feature 
in the data set. We have to choose a feature as the response, some others as predictors. 
And investigate if the relationship between them is linear or not.
Get the overall relationship between all pairs of the Auto data set:

```{r}
set.seed(100)
pairs(Auto)
```

From the plot above we can see when using mpg as the response, there are clear relationships between it and cylinders, displacement, horsepower, weight. Now we will find
out if they are nonlinear or not.

```{r}
fit1 <- lm(mpg~ poly(cylinders,2)+poly(displacement,5)+poly(horsepower,5)+poly(weight,5)
           , data =Auto )
summary(fit1)
```

The results show that there’s no significant relationship between mpg and cylinders. 
There’s weak relationship (p-value: 0.028) between mpg and displacement. There’s strong
quadratic relation between mpg and horsepower. There’s strong linear relation between 
mpg and weight.

Testing the degree with ANOVA

```{r}
an1 <- gam(mpg~ displacement+horsepower+weight, data=Auto)
an2 <- gam(mpg~ displacement+s(horsepower,2)+weight, data=Auto)
an3 <- gam(mpg~ s(displacement,5)+s(horsepower,5)+s(weight,5), data=Auto)

anova(an1,an2,an3, test='F')

summary(an3)
par(mfrow=c(1,3))
plot.Gam(an3, se=3, col='Blue')
```

According to plot of anv3, try quadratic with displacement and horsepower, linear with
weight:

```{r}
an4 <- gam(mpg~ s(displacement,3)+s(horsepower,3)+weight, data=Auto)
plot.Gam(an4,se=3,col='Green')
```

an4 looks good enough

No lets compare their test MSE

```{r}
lm1 <- glm(mpg~ displacement+horsepower+weight, data = Auto)
lm2 <- glm(mpg~ poly(displacement,3)+poly(horsepower,3)+weight, data=Auto )
lm3 <- glm(mpg~poly(displacement,5)+poly(horsepower,5)+poly(weight,5), data=Auto)

cv.glm(Auto,lm1, K=10)$delta[1]
cv.glm(Auto,lm2, K=10)$delta[1]
cv.glm(Auto,lm3, K=10)$delta[1]

```

The results also suggest model lm2 (same with anv4) is good enough.
So the conclusion of relationships with mpg: mpg ~ displacement: cubic; 
mpg ~ horsepower: cubic; mpg ~ weight: linear.
